\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-07-05 paper/paper.tex
Added a thank you note to Tom Collins
added cjs affil, mellon funding, spellcheck

\author[1]{Colin Raffel}
\author[1]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2,3]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}
\affil[3]{Center for Urban Science and Progress\\New York University, New York}

@@

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting, MIREX has become critically useful for tracking progress in MIR research.
MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
%
%Due to its scale, characteristics, and intended use, 
In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
Instead, researchers often create their own implementations of common metrics for evaluating their algorithms.
These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.

@@

Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in MIREX 2005 \cite{polinerMelodyEval}:
\textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
\textbf{Voicing False Alarm Rate} which computes the proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm;
\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (\ie{} within half a semitone of the reference frequency);
\textbf{Raw Chroma Accuracy} where the estimated and reference $f_0$ sequences are mapped onto a single octave before computing the raw pitch accuracy;
and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same timebase.

@@

When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common timebase.
In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all structure annotation metrics, as specified in \cite{willis2013mirex}.

@@

The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
This corroborates the need for transparency and community involvement in comparative evaluation.
The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
By encouraging MIR researchers to use the same easily understandable evaluation codebase, we can ensure that different systems are being compared fairly.

While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

@@

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.  Support provided in part by NSF grant IIS-1117015.

>>>>

\author[1]{Colin Raffel}
\author[1,4]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2,3]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
\affil[4]{Center for Jazz Studies\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}
\affil[3]{Center for Urban Science and Progress\\New York University, New York}

@@

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting, MIREX has become critically useful for tracking progress in MIR research.
MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA code-base includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
%
%Due to its scale, characteristics, and intended use, 
In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
Instead, researchers often create their own implementations of common metrics for evaluating their algorithms.
These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.

@@

Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in MIREX 2005 \cite{polinerMelodyEval}:
\textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
\textbf{Voicing False Alarm Rate} which computes the proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm;
\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (\ie{} within half a semitone of the reference frequency);
\textbf{Raw Chroma Accuracy} where the estimated and reference $f_0$ sequences are mapped onto a single octave before computing the raw pitch accuracy;
and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same time-base.

@@

When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common time-base.
In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all structure annotation metrics, as specified in \cite{willis2013mirex}.

@@

The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
This corroborates the need for transparency and community involvement in comparative evaluation.
The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
By encouraging MIR researchers to use the same easily understandable evaluation code-base, we can ensure that different systems are being compared fairly.

While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the code-base using the Pull Request feature.
With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

@@

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels and Tom Collins
for sharing his MATLAB implementation to evaluate musical patterns. Support provided in part by The Andrew~W.~Mellon Foundation, and NSF grant IIS-1117015.
